Multivariate Density Estimation: Comparing Transformation Random Forest, Normalizing Flows and Copulas

### 2025-09-30 report/MSc_Report.tex
.

\paragraph{Bridge to Chapter~\ref{ch:conclusion}.} The real-data study closes Chapter~\ref{ch:dataanalysis} by positioning separable triangular transports and TRTF within the UCI and MiniBooNE landscape. TRTF offers exact inversion, linear evaluation, and transparent conditional structure, yet trails modern flows on MiniBooNE. Chapter~\ref{ch:conclusion} interprets these trade-offs and distills guidance for practitioners choosing between separable transports, transformation forests, and copula baselines on tabular data.

>>>>

 The real-data study closes Chapter~\ref{ch:dataanalysis} by positioning separable triangular transports and TRTF within the UCI and MiniBooNE landscape. TRTF offers exact inversion, linear evaluation, and transparent conditional structure, yet trails modern flows on MiniBooNE. Chapter~\ref{ch:conclusion} interprets these trade-offs and distills guidance for practitioners choosing between separable transports, transformation forests, and copula baselines on tabular data.
